---
title: "Visual Search and Pre-crastination"
author: "Alasdair D.F. Clarke"
date: '2022-05-30'
output:
  tufte::tufte_html:
    number_sections: true
    fig_height: 3
    link-citations: yes  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
set.seed(2022)
```

```{r, message=FALSE}
# attach packages
library(rethinking)
library(tidyverse)
library(patchwork)
library(binom)
```

```{r}
# set ggplot2 options
theme_set(ggthemes::theme_tufte() + 
            theme(plot.background = element_rect(fill = "#fffff8", 
                                                 colour = "#fffff8")))

our_cols <- c("#1b9e77", "#7570b3")
options(ggplot2.discrete.fill = our_cols ,
        ggplot2.discrete.colour = our_cols)
```


# Import data

```{r}
dat_s <- read_csv("scratch/dat_rt_acc_strat.csv")

dat_p <- read_csv("scratch/prcrastination_and_personality.csv") %>%
  filter(!is.na(pre_crastinate)) %>%
  mutate(pre_crastinate = as_factor(pre_crastinate),
         pre_crastinate = fct_relevel(pre_crastinate, "no", "intermediate", "yes"))

```

# Overview of measures

## Visual Search Accuracy & Response Time

```{r}
# merge search with personality and precrastination data
dat <- left_join(dat_s, dat_p) %>%
  filter(!is.na(pre_crastinate))

dat %>% ggplot(aes(targ_side_rel, accuracy, fill = pre_crastinate)) +
  geom_boxplot(alpha = 0.5) +
    scale_x_discrete("trial type")  +
  theme(legend.justification=c(0,0), legend.position=c(0,0))  -> plt_acc

dat %>% ggplot(aes(targ_side_rel, median_rt, fill = pre_crastinate)) +
  geom_boxplot(alpha = 0.5) +
  theme(legend.position = "none") + 
  scale_x_discrete("trial type")  +
  scale_y_log10("reaction time (seconds)")  -> plt_rt

plt_acc + plt_rt

ggsave("scratch/acc_main.pdf", plt_acc + theme_bw() + theme(legend.position = "none"), width = 4, height = 3)
ggsave("scratch/rt_main.pdf", plt_rt  + theme_bw() + theme(legend.justification=c(1,0), legend.position=c(1,0)), width = 4, height = 3)

```



```{r}
rm(plt_acc, plt_rt)
```

## Search Strategy & Pre-crastination 

```{r}
dat_s %>% 
  group_by(person) %>%
  summarise(search_strat = unique(prop_hard)) -> dat_strat 

dat_strat %>%
  ggplot(aes(search_strat)) + 
  geom_histogram(breaks = seq(0.0, 1, 0.1), colour = "black") + 
  scale_x_continuous("search strategy score") -> plt

ggsave("scratch/strat_hist.pdf", plt + theme_bw() + theme(legend.position = "none"), width = 4, height = 3)

```

And now look at pre-crastination measure. 

```{r}

dat_p %>% ggplot(aes(x = n_pc)) +
  geom_histogram(bins = 7, alpha = 0.67, colour = "black") +
  scale_x_continuous("number of trials") + 
  scale_fill_viridis_d() +
  theme(legend.position = "none") -> plt1

dat_p %>% ggplot(aes(x = pre_crastinate)) + 
  geom_bar() +
  scale_x_discrete("pre-crastination classification") + 
  scale_fill_viridis_d() +
  theme(legend.position = "none") -> plt2

plt1 + plt2

ggsave("scratch/pre_crastinate.pdf", plt2 + theme_bw(),  width = 4, height = 3)

```

We have replicated the original pre-crastination finding.... 

```{r}
n_row <- nrow(dat_p)

dat_p %>% 
  group_by(pre_crastinate) %>%
  summarise(n = n(),
            percentage = 100*n/n_row) %>%
  knitr::kable()

rm(n_row)
```

# Registered Analysis

## Main Hypothesis

Is there a link betweeen pre-crastination and visual search strategy

### Pilot Data

First, we will rerun the model with the old pilot data. This is to double check the analysis pipeline is working properly.

```{r, results = "hide", message=FALSE, results = "hide"}
source("my_model_functions.R")

d_pilot <- read_csv("../pilot_experiment/level3_summary.csv",
                    show_col_types = FALSE) %>%
  mutate(pre_crastinate = as_factor(
    ifelse(pre_crastinate == 0, "no", "yes"))) %>%
  rename(search_strat = "opt_strat")

m_pilot <- fit_model(d_pilot)
```

```{r}
# generate prior only plot
plt <- gen_plot_pred(d_pilot, m_pilot, TRUE)
ggsave("scratch/pilot_prior_plot.pdf", plt, width = 5, height = 4)

plt2 <- gen_plot_pred(d_pilot, m_pilot)

plt + plt2
ggsave("scratch/pilot_plot.pdf", plt2, width = 5, height = 4)
```

### Full Data

Now run the model on the full data
```{r, results = "hide"}
d <- dat %>% select(prop_hard, pre_crastinate) %>%
  filter(pre_crastinate != "intermediate") %>%
  rename(search_strat = "prop_hard")


m_full <- fit_model(d)
```

```{r}
# generate prior only plot

plt <- gen_plot_pred(dat, m_full)
plt
ggsave("scratch/post_plot.pdf", plt + theme(legend.position = "none"), width = 4, height = 3)
```

# Now compute some summaries of the model posterior:

```{r}
samples <- rstan::extract(m_full)

pred_dat <- tibble(pre_crastinate = c(-0.5, 0.5))

X = as.matrix(pred_dat)
X <- cbind(1, X)

# Look at prior predictions for mmu
mu <- array(0, dim = c(100000, nrow(X)))
for (ii in 1:100000) {
	# generate a random beta from priors
	beta <- as.vector(c(
		rnorm(1, mean=0, sd=.5), 
		rnorm(1, mean=0, sd=.1)
		))
	mu[ii, ] <- plogis(X %*% beta)
}


mu_df <- tibble(
	pre_crastinate = rep(c("no", "yes", "difference"), each = 100000),
	mu  = c(mu[,1], mu[,2], mu[,2] - mu[,1]))


HPDI(mu[,2] - mu[,1], 0.95)
mean(abs(mu[,2] - mu[,1]) > 0.05)
mean((mu[,2] - mu[,1]) > 0)
```

## Pre-crastination & Conscientiousness

```{r}
my_cols <-  c(viridis::viridis(3)[1], "#444444", viridis::viridis(3)[3], viridis::viridis(3)[2],  "#999999")

dat_p %>% filter(!is.na(pre_crastinate), !is.na(conscientiousness)) %>%
  ggplot(aes(pre_crastinate, conscientiousness, fill = pre_crastinate)) + 
  geom_boxplot(alpha = 0.5) +
  scale_fill_manual("pre-crastinate", values = my_cols) -> plt

plt

ggsave("scratch/pre_cras_consc.pdf", plt+theme_bw(), width = 4, height = 3)

cor.test(dat_p$conscientiousness, dat_p$n_pc)

# now to it with Bayes
library(brms)
m <- brm(n_pc ~ conscientiousness, data = dat_p,
               priors = c(prior()))

```
